Title

### 2023-05-16 main.tex
Otros cambios

This theorem implies that starting from the state $|0\rangle$,
the only curves we could expect to create
with a 1PR circuit are those of the form
\begin{equation}
|\eta(p)\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\label{eq:curve-states}
\end{equation}
with 
\begin{equation}
|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{are orthogonal vectors}.
\label{eq:conditions-vecs}
\end{equation}
Furthermore, we can show a way to create these curves of states
with a 1PR circuit.
To do it, we can use the circuit of \fref{fig:1PR-circuit} with the parametrized
rotation on the last qubit controlled by all the others
and with matrices $A$ and $B$ defined as:
\begin{align*}
B = (\vec{d}, *,*, \cdots,*), \; 
A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|).
\end{align*}
Here the column vector $\vec{d}$ is defined as 
$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)$
and the asterisks can be completed in any
way such that these matrices are unitary.
Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
and applying the matrices $ARB$ defined
like this, some calculations lead us to 
the resulting curve of states
of \eref{eq:curve-states}.

@@

\tbnote{Sección no escrita del todo aún, sólo es un medio resumen que tenía.}
We can now use the last theorem to conclude directly which Pauli dynamical maps
can be created using a 1PR circuit.
For 1PR circuits, the ancilla state of \ref{fig: circuit-pauli} 
has to be created with only one parametrized curve. Therefore, theorem 2 implies that a map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is}
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

For the particular case of one qubit,
we show some examples of Pauli dynamical maps that can be
implemented with a 1PR circuit, which are plotted
in \fref{fig:curves}.

@@

\begin{itemize}
\item \textbf{Bit flip map:} 
This Pauli dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of state $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = (\sqrt{1-p},\sqrt{p},0,0).
\end{align*}
This curve can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is} \left( \dfrac{1}{2}, - \dfrac{i}{2},0,0 \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2},0,0 \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$.
Therefore, we can see that the curve satisfies the conditions of theorem 2 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps
changing $\sigma_1$ with
$\sigma_3$ and $\sigma_2$ respectively.

\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, taking the $\beta_j$ to be real,
the curve of states needed to create on the ancilla qubits is
\begin{align*}
|\beta(p) \rangle = \left( \sqrt{1-3p/4}, \sqrt{p/4}, \sqrt{p/4},\sqrt{p/4} \right).
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle = e^{is} \left( \dfrac{1}{2}, \dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}} \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}}\right)
\end{align*}
with $s = \arcsin(\sqrt{3p/4}$.
We can see that the curve satisfies the conditions of theorem 2, which
means that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} Finally, we define a parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2 \sigma_0 \rho \sigma_0 + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
this dynamical map can be implemented
by creating the curve of states:
\begin{eqnarray}
|\beta(p)\rangle = \left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right).
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle = \left( \dfrac{1}{2},0,0, \dfrac{1}{2} \right) + e^{is} \left( \dfrac{i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{-i}{4} \right) + e^{-is}  \left( \dfrac{-i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{i}{4} \right),
\end{align*}
with $s = \arcsin(p)$, so that
this map fulfills the conditions of theorem 2.
\end{itemize}

We can construct other examples of 
Pauli dynamical maps
such that the curve of states $|\beta(p)\rangle$ requires
can be implemented with a 1PR circuit.
To do it, we only need to choose the three vectors $\vec{a}, \vec{b},\vec{c}$
that satisfy the conditions of theorem 2.

This can be done systematically for the case of curves of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|\vec{a}|, |\vec{b}|, |\vec{c}|$
such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$
by choosing two angles $\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and 
defining:
\begin{align*}
|\vec{a}| = \sin \nu \cos \mu, \; |\vec{b}| = \sin \nu \sin \mu , \; |\vec{c}| = \cos \nu.
\end{align*}
\item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
\item[3.] We select a unitary matrix $U$
whose first row is $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$,
with $\theta \in [0,2\pi]$ and use it to define $\vec{a} = U \vec{a'}, \vec{b} = U \vec{b'}, \vec{c} = U \vec{c'}$.

This way, since the primed vectors are orthogonal and their squared norms add up to one,
so do the unprimed vectors. 
Moreover, we have that $\vec{a}+ \vec{b}+ \vec{c} = (e^{i\theta},0,0,0)$,
which is a consequence of the first row of $U$ being $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$ because:
\begin{align*}
\vec{a} + \vec{b} + \vec{c} = U (\vec{a'} + \vec{b'} + \vec{c'}) = U(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $U(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $U$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
one but $U$ preserves the norm.
\end{itemize}

Following this procedure for random
angles and unitary matrices $U$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves-random}.

>>>>

This theorem implies that starting from the state $|0\rangle$,
the only curves of states we could expect to create
with a 1PR circuit are those of the form
\begin{equation}
|\eta(p)\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\label{eq:curve-states}
\end{equation}
with 
\begin{equation}
|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{orthogonal vectors}.
\label{eq:conditions-vecs}
\end{equation}
Furthermore, we can exhibit a way to create any of these curves of states
with a 1PR circuit.
To do it, we can use the circuit of \fref{fig:1PR-circuit} with the parametrized
rotation $R$ on the last qubit controlled by all the other qubits
and matrices $A$ and $B$ defined as:
\begin{align*}
B = (\vec{d}, *,*, \cdots,*), \; 
A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|).
\end{align*}
Here the column vector $\vec{d}$ is defined as 
$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)^T$
and the asterisks can be completed in any
way such that these matrices are unitary.
Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
and applying the matrices $ARB$ defined
like this, some direct calculations lead us  to 
the resulting curve of states
of \eref{eq:curve-states}.

@@

We can now use the last theorem to conclude directly which Pauli dynamical maps
can be implemented using a 1PR circuit.
With this condition, the curve of states of \eref{eq: parametrized state} 
has to be created on the ancilla qubits with only one parametrized curve. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

For the particular case of one qubit,
we can show some examples of Pauli dynamical maps that can be
implemented with a 1PR circuit, which are plotted
in \fref{fig:curves}.

@@

\begin{itemize}
\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \left(\sqrt{1-p},\sqrt{p},0,0\right).
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is} \left( \dfrac{1}{2}, - \dfrac{i}{2},0,0 \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2},0,0 \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps
changing $\sigma_1$ with
$\sigma_3$ and $\sigma_2$ respectively.

\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, taking the $\beta_j$ to be real,
the curve of states needed to create on the ancilla qubits is
\begin{align*}
|\beta(p) \rangle = \left( \sqrt{1-3p/4}, \sqrt{p/4}, \sqrt{p/4},\sqrt{p/4} \right).
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle = e^{is} \left( \dfrac{1}{2}, \dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}} \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}}\right)
\end{align*}
with $s = \arcsin(\sqrt{3p/4})$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} Finally, we define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2 \sigma_0 \rho \sigma_0 + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{eqnarray}
|\beta(p)\rangle = \left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right).
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle = \left( \dfrac{1}{2},0,0, \dfrac{1}{2} \right) + e^{is} \left( \dfrac{i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{-i}{4} \right) + e^{-is}  \left( \dfrac{-i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{i}{4} \right),
\end{align*}
with $s = \arcsin(p)$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.
\end{itemize}

Furthermore, we can construct other examples of 
Pauli dynamical maps
such that the curve of states $|\beta(p)\rangle$ 
can be implemented with a 1PR circuit.
To do it, we only need to choose the three vectors $\vec{a}, \vec{b},\vec{c}$
that satisfy the conditions of  \eref{eq:conditions-vecs}.

For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|\vec{a}|, |\vec{b}|, |\vec{c}|$
such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$
by selecting two angles $\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and 
defining:
\begin{align*}
|\vec{a}| = \sin \nu \cos \mu, \; |\vec{b}| = \sin \nu \sin \mu , \; |\vec{c}| = \cos \nu.
\end{align*}
\item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
\item[3.] Finally, we select a unitary matrix $V$
and use it to define the vectors $\vec{a} = V \vec{a'}, \vec{b} = V \vec{b'}, \vec{c} = V \vec{c'}$.
This way, since the primed vectors are orthogonal and their squared norms add up to one,
so do the unprimed vectors and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
These maps where constructed with the additional condition
of passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $(e^{i \theta},0,0,0)$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
\vec{a} + \vec{b} + \vec{c} = U (\vec{a'} + \vec{b'} + \vec{c'}) = U(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $U$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
one but $V$ preserves the norm.
